\subsection{Evaluation of Anki}

Anki is a system for spaced learning. It works by organising facts (in a wide
sense, like foreign words or parts of a map) into individual cards, which in
part constitute a deck of facts about a given topic. The user plays through the
deck by going through each card and stating how easy it was to recall the fact.
The software then replays cards depending on how good or bad the recall was
until some threshold of recollection has been met. Bad recall would result in 
the card appearing more often, and vice versa. This algorithm is inspired by the
SuperMemo system written in the 1980s\cite{ankimanual}. The intuition is that 
we reinforce learning by recalling something just as we are about to forget 
about it.

Users are allowed to share, amend, or extend existing decks. While Anki
primarily exists for the purpose of individual learning, the composable and
free software format allows for others to take part in the learning 
experience. The software has enjoyed great popularity amongst several groups, 
most notably learners of foreign languages.

Anki is available both as a desktop client and through a web interface --- 
AnkiWeb\footnote{https://ankiweb.net/}. While the latter easily allows for 
online sharing of decks, it doesn't allow for importing them. This is because 
it only synchronises with the desktop client. This highlights the challenges 
faced by desktop and web clients with different capabilities, and the value of 
isomorphic implementations.

AnkiWeb allows for synchronization and sharing of card decks (as files) using 
a free online service. It is also able to play through the decks, but not 
import them from stand-alone files.

The desktop client of Anki will therefore be the main focus of this evaluation,
as it is the only full implementation of the system. Similar software in the
same area are SuperMemo and Fluxcards.

In terms of licensing, Anki is well-aligned with our project. It is freely 
licensed under the terms of the GNU AGPL v3+. Sub-components are licensed 
under a variety of licenses, mostly GNU GPL and flavours of BSD/MIT licences. 
All art assets are also freely licensed.

\subsubsection{Expressiveness}

Anki allows for the authoring of (decks of) flashcards using standard HTML
components with CSS styling. As a result, users are able to enrich cards with
customised formatting, sound, and video. The users are also able to record their
own voice (and repeat sounds) during playthrough. This offers an interactive
experience to the end-user. Since HTML and CSS are relatively flexible and
well-documented technologies, and is used by many other prominent parties, 
this is likely a good choice by the Anki developers, that gives the users a 
good balance between expressiveness and ease of use, as well as familiarity.

\subsubsection{Ease of use}

Because the technologies used by Anki are freely available and readily
documented, they constitute an open standard. This open container format makes
Anki composable, and since the technologies are rather common (at least HTML),
users can make relatively simple changes without any major obstacles.

However, Anki is considered to have a poor user interface interaction story 
for common scenarios\cite{pcworldanki}.

An example of a problematic story is the rather common case of wanting to share
a deck. This usually has to be done through AnkiWeb, a free online service, 
which allows the user to download new decks made by other users. However, no such
suggestion is made to the user. Thus, the social dimension of Anki is 
downplayed.

Similarly, when using the software for the first time, the user is greeted by 
a shallow window with a single deck, and no explanation of Anki or its 
algorithm is given. The user can click a simple built-in test deck to play 
through it, but this is not suggested by the software, and the deck does not 
showcase Anki's capabilities either (for example the use of rich media or 
LaTeX equations).

Other examples include the main window, which has both a menu bar and some
buttons. One of the buttons suggests that the user might be able to import new
decks, but turns out to be about constructing new decks.

The most complex interface in Anki is the library view. It allows for somewhat
non-trivial querying of all the decks in use, with numerous built-in categories
and tags for distinguishing them (be it difficulty, topic, or the decks
scheduled for today). Also, this rich view is not offered in AnkiWeb, so there's
an inherent divide in the capabilities of searching already imported decks and
looking for new ones, limiting the ability to explore.

Universal design isn't guaranteed since the decks are made by users. There 
doesn't appear to be any way of filtering decks based on accessibility, nor 
any user-interface encouragement to \emph{do} universal design when authoring 
decks.

\subsubsection{Takeaway points}

\begin{itemize}
\item Anki offers spaced repetition learning, which is an established and 
  useful way of learning.
\item The simple metaphor (a deck of flashcards) is intuitive and easy to 
    explain to users\cite{burke2002s}, and simple enough to implement.
\item Anki's use of HTML elements provides a universal container format and
  facilitates sharing. However, the web interface is very limited, and while it
  does allow for sharing, it does not allow for importing decks, thus not
  providing a full (isomorphic) user experience across platforms.
\item The desktop client has a problematic user interface story, and does not
  provide enough directions or examples for effective use. Modal dialogues and
  context switching might provide a more elegant solution for capturing common
  usage patterns (compared to displaying the full set of choices and categories
  available to the user, e.g.\ in the library view).
\end{itemize}
