\subsection{Evaluation of LateralGM and ENIGMA}

LateralGM\footnote{https://github.com/IsmAvatar/LateralGM} is a free tool to 
author and edit games. It aims to be compatible with the file formats of Game 
Maker and the newer GameMaker: Studio, and has a user interface very similar 
to that of Game Maker. To compile and run games, LateralGM normally interfaces 
with ENIGMA\footnote{http://enigma-dev.org/}, which is a compiler and runtime 
system aiming to be backwards compatible with Game Maker games.

\subsubsection{Expressiveness}
LateralGM and ENIGMA form a multi-genre game authoring tool with features that 
make it easy to use for beginners, but also powerful for advanced users. 
Although the scripting language has some support for 3D 
graphics\cite{enigma3d}, the software mainly focuses on 2D graphics and 
gameplay.

LateralGM presents the game as a set of different resources, including sounds, 
background images, sprites, scripts, fonts, objects, and rooms. Users may edit 
sounds and images within a game using external programs.

Objects may be programmed to act on various events. Events include the 
``step'' event (fired once in every update cycle, e.g.\ 30 times per second), 
user input, collision detection, timers, action-/script-triggered events, and 
many more\cite{lgmevents}. Each event can be programmed using either 
drag-and-drop actions or scripts. The set of drag-and-drop actions is 
extensive and includes basic flow control, and may also be extended with 
action libraries.

Each object can be set to use a possibly animated sprite, which causes each 
instance of the object to be drawn with that sprite. This sprite may also be 
used for collision detection. The ``draw'' event is also available for 
producing more advanced graphics. Objects may also be set as invisible, 
appearing in the room editor and possibly providing collision detection with 
the associated sprite, but not visible during gameplay.

The room editor allows users to graphically place instances of objects, either 
freely or in a configurable grid, inside a room as they will appear in the 
game. The user may define multiple layers of background and foreground images, 
either as whole images, possibly repeated or stretched, or in the form of 
placeable tiles, using the image as a tileset.

LateralGM loads and saves games in the proprietary file formats of various 
versions of Game Maker. These file formats are not officially documented, but 
have been reverse-engineered by LateralGM developers\cite{lgmformats}. While 
LateralGM and ENIGMA aim to be compatible with both current and earlier 
versions of Game Maker and GameMaker: Studio, several of these versions of 
Game Maker have incompatibilities between themselves. Not all features are 
implemented in LateralGM and ENIGMA, and development is struggling to catch up 
with later versions while still being compatible with earlier versions.

\subsubsection{Ease of use}
LateralGM lets users make simple games without writing a single line of code, 
using only drag-and-drop actions and graphically placing object instances in 
each room. Parametres to the actions may be given as scripting language 
expressions, providing a smooth learning curve from simple actions to the full 
scripting language.

\subsubsection{Takeaway points}

\begin{itemize}
\item Drag-and-drop can be used together with a written programming language 
    for a very smooth learning curve for non-programmers.
\item Trying to keep up compatibility with proprietary tools and undocumented 
    file formats is difficult and may take more development resources than 
    available.
\end{itemize}
